Lake Photic Zone Temperature accross the Conterminous United States

### 2019-08-09 manuscript/manuscript.Rmd
Added paragraph to discussion

In addition to the several average air temperature variables, we included land-use/land cover variables.  Specifically, we calculated the percent impervious surface for a 3km lake buffer and a measure of shoreline development (need to look at Jeff’s package to see how this measured).  This variables were included based on the assumption that higher amounts of development and therefore impervious surface surrounding a lake would lead to higher temperatures in lakes.  Yet neither of these variables were selected in the final model.  Even though the land-use variables were not selected that does not mean development and impervious were not impactful.  This urban-heat effect on lakes may have been adequately captured in the average ambient air temperature.  Therefore, making the land-use variables redundant.  Regardless these variables did not independently contribute to the model’s accuracy.

>>>>

In addition to the several average air temperature variables, we included land-use/land cover variables.  Specifically, we calculated the percent impervious surface for a 3km lake buffer and a measure of shoreline development (need to look at Jeff’s package to see how this is measured).  This variables were included based on the assumption that higher amounts of development and therefore impervious surface surrounding a lake would lead to higher temperatures in lakes.  Yet neither of these variables were selected in the final model.  Even though the land-use variables were not selected that does not mean development and impervious were not impactful.  This urban-heat effect on lakes may have been adequately captured in the average ambient air temperature.  Therefore, making the land-use variables redundant.  Regardless these variables did not independently contribute to the model’s accuracy.

Insert paragraph on model shortcomings

An advantage of this model is that we are now able to forecast and backcast lake photic zone temperature.  While there are numerous lakes that have substantial historical temperature data, these data are not consistently available for large regions.  This inhibits our ability to make large scale predictions about changes to lake dynamics (e.g., stratification and mixing) and ecological risk (e.g., anticipated changes in cyanobacteria bloom frequency).  At the continental scale, essentially, we could identify area that might have a higher ecological risk.  Yet if there was an individual lake of concern that lack temperature, this model would be as effective.

Final paragraph
